\documentclass[12pt]{article}
\usepackage[margin=0.5in]{geometry}  % page margins
\usepackage{enumitem}
\usepackage{hyperref}  % hyperlinks
\usepackage[parfill]{parskip}  % disable paragraph indent
\nofiles  % don't generate .aux, etc.
\pagenumbering{gobble}  % remove page numbering

% Resume section heading
\newcommand{\rSection}[1]{
    \medskip
    {\Large #1}
    \medskip
    \hrule
}


% Custom resume item
\newcommand{\rItem}[2]{
    \item \textbf{#1:} #2
    \vspace{-5pt}
}

\begin{document}


\begin{center} 
    \textbf{\Huge chariotsofiron} \\
    \vspace{5pt}
    \href{https://www.github.com/chariotsofiron}{github.com/chariotsofiron}
\end{center}
\vspace{-15pt}


\rSection{About me}
\begin{itemize}[label={},leftmargin=0pt]
    \item{
        \textbf{Languages:} Python, Rust, C++, Java, SQL
        \hfill
        \textbf{Tools:} Git, AWS, Docker, sqlite, Numpy, Pandas
        \vspace{-5pt}
    }
    \item{
        \textbf{Interests:} Bouldering, A24 films, Golf, Chess
        \hfill
        \textbf{Legal status:} Canadian, eligible for TN status
        \vspace{-5pt}
    }
\end{itemize}


\rSection{Experience}

\textbf{Akuna Capital} \hfill Chicago IL, US\\
Quantitative Developer \hfill Jul 2022 - Present\\
Junior Quantitative Developer \hfill Feb 2021 - Jun 2022\\
Quantitative Developer Intern \hfill Jun 2020 - Aug 2020\\
\vspace{-18pt}
\begin{itemize}[leftmargin=13pt]
    \item Conducted research on methods of reducing network latency to the C++ market-data engine, leading to several millisecond performance gains on Binance and other exchanges.
    \vspace{-5pt}
    \item Built a service to automate and optimize capital allocation across exchanges by initiating on-chain transactions. Developed a linear programming algorithm in Python to minimize network fees.
    \vspace{-5pt}
    \item Improved reliability of the trading engine by developing a protocol for reconciling order states when receiving unreliable market data.
    \vspace{-5pt}
    \item On-boarded and managed a summer intern. Designed a project for them and supervised its completion.
\end{itemize}


\textbf{Apption Software} \hfill Ottawa, ON, Canada\\
Data Science Intern \hfill Jan 2018 - Apr 2018\\
Performed data analysis on procurement contract life-cycle data to identify trends and relationships. 


\textbf{Peraso Technologies} \hfill Toronto, ON, Canada\\
Software Engineer Intern \hfill May 2017 - Aug 2017\\
Developed high-performance, low-latency firmware for multi-gigabit wireless embedded devices in C++.


\rSection{Projects}
\begin{itemize}[label={},leftmargin=0pt]
    \setlength\itemsep{0em}
    \rItem{C Compiler}{Wrote a compiler for a subset of C, featuring loops, arrays, structs, and functions. It generated bytecode that could be interpreted by a virtual machine, or compiled to a CPU I designed.}
    \rItem{Natural language processing}{Generated trading signals based on a weighted sentiment analysis of experts, identified by web scraping social media accounts and comments online.}
    \rItem{Trivia Question Solver}{Developed a multiple-choice question solver for a popular trivia app using OpenCV to parse text from screenshots and NLTK to generate and rank search engine queries.}
\end{itemize}


\rSection{Awards and Scholarships}
\begin{itemize}[label={},leftmargin=0pt]
    \rItem{Fulbright Scholarship (\$8,000)}{Studied maths and machine learning at Ithaca College, NY.}
    \rItem{NSERC USRA (\$6,000)} {Worked on WiGig wireless chipsets at Peraso.}
    \rItem{Rotman International Trading Competition (2019)} {Placed 5th out of 52 schools. Developed algorithms and quantitative models to trade options, fixed-income, and commodities.}
\end{itemize}



\rSection{Education}
\textbf{University of Ottawa} \hfill Ottawa, ON, Canada\\
BSc. Joint Honours in Computer Science and Mathematics, GPA: 3.9/4.0 \hfill Sep 2016 - Dec 2020\\
First place honors project: Deep RL for combinatorial games with exponential action spaces.
\vspace{-5pt}

\end{document}
